---
title: "HW 5"
author: "Sam Loewen"
date: "11/3/2019"
output: github_document
---

```{r setup}

library(tidyverse)
library(rvest)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

# Problem 1

```{r}
fill_in_values = function(x){
 
  if(is.numeric(x) == T) {
    x[is.na(x)] = mean(x, na.rm=T)
    }
  if(is.character(x) == T){
    x[is.na(x)] = replace_na("virginica")
    }

  return(x)
 
}

iris_with_missing <- map_df(iris_with_missing,fill_in_values)
```

#Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.





