---
title: "p8105_hw5_scl2160"
author: "Sam Loewen"
date: "11/3/2019"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(rvest)
```

# Problem 1

```{r}
set.seed(1)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
fill_in_values = function(x){
 
  if(is.numeric(x) == T) {
    x[is.na(x)] = mean(x, na.rm=T)
    }
  if(is.character(x) == T){
    x[is.na(x)] = replace_na("virginica")
    }

  return(x)
 
}

iris_with_no_missing = map_df(iris_with_missing, fill_in_values)
```


# Problem 2

```{r}
set.seed(1)

file_list = list.files("./data", pattern= "*.csv")

study_data = map_df(paste("./data", file_list, sep = "/"), read_csv) %>% 
  mutate(file_name = file_list) %>% 
  separate(file_name, c("study_arm", "study_id", "csv")) %>% 
  select(study_arm, study_id, week_1:week_8, -csv) %>% 
  mutate(study_arm = ifelse(study_arm == "con", "control", "experimental"),
         study_id = c(1:20))

study_data %>% 
  pivot_longer(week_1:week_8,
    names_to = "week",
    values_to = "obs")%>% 
  ggplot(aes(x=week, y=obs, group = study_id, color = study_arm)) + geom_point() + geom_line() +
  labs(title = "Observations over time, by study arm", 
    x = "week", 
    y = "observations")

```

The control group consistantly had lower scores than the experimental group. The experimental group seemed to score higher over time, whereas the control group stayed relatively level.

# Problem 3

```{r}
set.seed(1)
p3_data = function(n=30, beta0=2, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, 0, 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50))
  )
  
  ls_fit = lm(y ~ x, data = sim_data) %>% 
    broom::tidy()
  
  tibble(
    beta1_hat = ls_fit[[2,2]],
    beta1_p = ls_fit [[2,5]]
    
    )
}

sim_results = rerun(10000,p3_data(beta1 = 0)) %>% 
  bind_rows()

sim_results_all_b1 = 
  tibble(beta_1 = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_list = map(.x = beta_1, ~ rerun(10000, p3_data(beta1 = .x))),
    output_df = map(output_list, bind_rows)) %>% 
  select(-output_list) %>% 
  unnest(output_df)
```


```{r}
sim_results_all_b1 %>% 
  mutate(reject_null = ifelse(beta1_p<.05,1,0)) %>% 
  group_by(beta_1) %>% 
  summarize(power = mean(reject_null)) %>% 
  ggplot (aes(x = beta_1, y = power)) + geom_point() + geom_line() +
  labs(title = "Power by beta1 value", 
    x = "beta1 value", 
    y = "Power")
```

Power increases as effect size increases.

```{r}
sim_results_all_b1 %>% 
  group_by(beta_1) %>% 
  summarize(avg_b1_hat = mean(beta1_hat)) %>% 
  ggplot (aes(x = beta_1, y = avg_b1_hat)) + geom_point() + geom_line() +
  labs(title = "beta1 vs beta1 hat", 
    x = "beta1 value", 
    y = "Average beta1 hat")
```

```{r}
sim_results_all_b1 %>% 
  mutate(reject_null = ifelse(beta1_p<.05,1,0)) %>% 
  filter(reject_null == 1) %>% 
  group_by(beta_1) %>% 
  summarize(avg_b1_hat = mean(beta1_hat)) %>% 
  ggplot (aes(x=beta_1, y=avg_b1_hat)) + geom_point() + geom_line() +
  labs(title = "beta1 vs beta1 hat among p<.05", 
    x = "beta1 value", 
    y = "Average beta1 hat") 
```

When we look at all cases, the sample average of β1 is appoximately equal to the true value of β1. However when we filter for cases in which the null hypothesis is rejected, the β1s are no longer equal. Our estiamted and true values are less similar in the second plot because we are filtering for cases where we would reject the null hypothesis, or cases where our outcome is significantly different from our expected value.

